---
title: "notesOnPackageCreation"
author: "Nolan"
date: "10/17/2021"
output: html_document
---

```{r setup, include=T}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup of package

Created a directory and created a package directory

```{r intitialPackageDevelopment, eval = F}
library("devtools")
library("roxygen2")
library("tidyverse")
library("fs")
library("usethis")

wd <- "Q:/Teaching/Computational Biology/Git"
pn <- "compBioFunctions"
dir.create(wd, showWarnings = F)
setwd(wd)
create_package(pn)
```

This started a new rstudio session according to my rstudio setting. The working directory was set to inside the pn directory nested inside the wd directory

My next step was to initialize github. An excellent guide for setting up github in R can be found at <https://kbroman.org/github_tutorial/>

```{r inititalizeGit, eval=F}
require(usethis)
usethis::use_github()
```

# Editing package

I then created a new R script file in the R directory named idToNumber.R, added a function, in R-studio went to "Code-\>Insert Roxygen Skeleton", and filled out text next to the parameters.

I then created this document and did my initial commitment if it:

-   I opened the git pane.

-   I marvelled for a second at the meta-ness of typing out what I was doing as I did it.

-   I then typed the rest of this based on what i planned to do.

    -   I clicked commit.

    -   I "staged" this Rmd file.

    -   Typed my initial commit message in the box and accepted the changes.

-   Clicked "push" (up-arrow).

Next I tried out installing from github in a different rstudio session (because I wasn't sure what would happen from inside the package session).

Okay, lets do some of this documentation stuff.

```{r setLicense, eval = F}
#Add the MIT license
usethis::use_mit_license()
```

```{r setDescription, eval = T}
#Edit the description file
descOptions <- list(
    Title = "Creates Functions for Nolan's Comp. Bio. Course",
    `Authors@R` = 'person("Nolan", "Bentley", email = "NolanBentley@utexas.edu", role = c("aut","cre","mai"))',
    Description = "This package loads functions for use in Nolan Bentley's Computational Biology Course and makes certain datasets available.",
    License = "MIT + file LICENSE"
)
usethis::use_description(descOptions)
print(readLines("DESCRIPTION"))
```

This Rmd file causes a note to appear in the checking.

```{r addThisRmdToRBuildIgnore}
addedToBuildIgnore <- c('LICENSE.md',
                        'compBioFunctions.Rproj',
                        'packageCreationNotes.html','packageCreationNotes.Rmd')
usethis::use_build_ignore(addedToBuildIgnore)
#The following was a chance discovery that sounds like a good idea
usethis::git_vaccinate()
```

I wanted to add some data that gets loaded

```{r addData, eval=F}
file.create("R/data.R")
usethis::use_data_raw("biol321Ids")
usethis::use_data_raw("humanGenes")

library("sinew")
write(sinew::makeOxygen(biol321Ids, add_fields = "source"),
      "R/data.R",append = T)
write(sinew::makeOxygen(biol321Ids, add_fields = "source"),
      "R/data.R",append = T)
```

I ran the following several times and added more stuff to the above until it no longer produced errors.

```{r rerunDocumentationAndCheck, error = T}
devtools::document()
devtools::check()
```

I now had done all my initial steps, so I then saved this, knit an html version, and committed the changes to files.
