---
title: "notesOnPackageCreation"
author: "Nolan"
date: "10/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Created a directory and created a package directory

```{r intitialPackageDevelopment, eval = F}
library("devtools")
library("roxygen2")
library("tidyverse")
library("fs")
library("usethis")

wd <- "Q:/Teaching/Computational Biology/Git"
pn <- "compBioFunctions"
dir.create(wd, showWarnings = F)
setwd(wd)
create_package(pn)
```

This started a new rstudio session according to my rstudio setting. The working directory was set to inside the pn directory nested inside the wd directory

My next step was to initialize github. An excellent guide for setting up github in R can be found at <https://kbroman.org/github_tutorial/>

```{r inititalizeGit, eval=F}
require(usethis)
usethis::use_github()
```

I then created a new R script file in the R directory named idToNumber.R, added a function, in R-studio went to "Code-\>Insert Roxygen Skeleton", and filled out text next to the parameters.
